---
title: "Make Reddit Great Again"
author: "Amaury Trujillo"
output: html_notebook
---

Please refer to the README in the notebook's repository for more information.

**Before continuing you should have read the corresponding paper to understand the notebook.**


```{r, setup, echo = FALSE, message=FALSE, warning=FALSE}
source("./common_variables.R", local = knitr::knit_global())
source("./db_utils.R", local = knitr::knit_global())
source("./data_wrangling.R", local = knitr::knit_global())
source("./plot_utils.R", local = knitr::knit_global())
```

```{r}
# r/The_Donald
td_submissions <- retrieve_db_table("the_donald", "submissions")
td_comments <- retrieve_db_table("the_donald", "comments")

# Core Users of r/The_Donald
ctd_subreddits <- retrieve_db_table("core_the_donald", "subreddits")
ctd_submissions <- retrieve_db_table("core_the_donald", "submissions")
ctd_comments <- merge(
  retrieve_db_table("core_the_donald", "comments"),
  retrieve_db_table("core_the_donald", "perspective_scores"),
  by.x = "id",
  by.y = "comment_id",
  all.x = TRUE
)

# Core Users W/I r/The_Donald
ctd_itd_submissions <- ctd_submissions[subreddit_id == the_donald_id]
ctd_itd_comments <- ctd_comments[subreddit_id == the_donald_id]

# Core Users W/O r/The_Donald
ctd_otd_submissions <- ctd_submissions[subreddit_id != the_donald_id]
ctd_otd_comments <- ctd_comments[subreddit_id != the_donald_id]

# Media Bias / Fact Check
mbfc <- fread("./data/mbfc_scores.csv")
```


## Daily activity

```{r}
td_daily_activity <- daily_activity(td_submissions, td_comments)
ctd_itd_daily_activity <- daily_activity(ctd_itd_submissions, ctd_itd_comments)
ctd_otd_daily_activity <- daily_activity(ctd_otd_submissions, ctd_otd_comments)

# Example
head(td_daily_activity)
```

```{r}
# Activity around quarantine 

td_q_daily_activity <- td_daily_activity[created_date <= post_q_end_date]
ctd_itd_q_daily_activity <- ctd_itd_daily_activity[created_date <= post_q_end_date]
ctd_otd_q_daily_activity <- ctd_otd_daily_activity[created_date <= post_q_end_date]

set_relative_week_and_day(td_q_daily_activity, quarantine_date)
set_relative_week_and_day(ctd_itd_q_daily_activity, quarantine_date)
set_relative_week_and_day(ctd_otd_q_daily_activity, quarantine_date)

# Activity around restriction

ctd_otd_r_daily_activity <- ctd_otd_daily_activity[created_date >= pre_r_start_date]
set_relative_week_and_day(ctd_otd_r_daily_activity, restriction_date)

# Example
head(td_q_daily_activity)
```


```{r}
# Interrupted Time Series

activity_col_names <- c("s_count", "c_count", "s_dau", "c_dau")
names(activity_col_names) <- activity_col_names
activity_col_list <- as.list(activity_col_names)

activity_its_lm <- function(dt) {
  lapply(activity_col_list, function(y_name) intervention_its_lm(dt, y_name))
}

td_q_daily_activity_its_lm <- activity_its_lm(td_q_daily_activity)
ctd_itd_q_daily_activity_its_lm <- activity_its_lm(ctd_itd_q_daily_activity)
ctd_otd_q_daily_activity_its_lm <- activity_its_lm(ctd_otd_q_daily_activity)
ctd_otd_r_daily_activity_its_lm <- activity_its_lm(ctd_otd_r_daily_activity)

# Example
td_q_daily_activity_its_lm$s_count
```

### Activity on r/The_Donald

```{r}
activity_its_plot(
    dt = td_q_daily_activity,
    col_suffix = "count",
    s_color = submission_color,
    c_color = comment_color,
    its_lm = td_q_daily_activity_its_lm,
    intervention = "quarantine",
    y_lab = "# Posts",
    scale_labels = c("submissions", "comments")
)
```

```{r}
# Effect on submissions
td_q_bsts_s_count <- intervention_bsts_effect(td_q_daily_activity, "quarantine", "s_count")

# Effect on comments
td_q_bsts_c_count <- intervention_bsts_effect(td_q_daily_activity, "quarantine", "c_count")

# Example
td_q_bsts_c_count
```


```{r}
activity_its_plot(
    dt = td_q_daily_activity,
    col_suffix = "dau",
    s_color = submission_users_color,
    c_color = comment_users_color,
    its_lm = td_q_daily_activity_its_lm,
    intervention = "quarantine",
    y_lab = "# DAU",
    scale_labels = c("submission DAU", "comments DAU")
)
```

```{r}
# Effect on submission DAU
td_q_bsts_s_dau <- intervention_bsts_effect(td_q_daily_activity, "quarantine", "s_dau")

# Effect on comment DAU
td_q_bsts_c_dau <- intervention_bsts_effect(td_q_daily_activity, "quarantine", "c_dau")
```

### Activity of Core Users W/I r/The_Donald

```{r}
activity_its_plot(
    dt = ctd_itd_q_daily_activity,
    col_suffix = "count",
    s_color = submission_color,
    c_color = comment_color,
    its_lm = ctd_itd_q_daily_activity_its_lm,
    intervention = "quarantine",
    y_lab = "# Posts",
    scale_labels = c("submissions", "comments")
)
```

```{r}
# Effect on submissions
ctd_itd_q_bsts_s_count <- intervention_bsts_effect(ctd_itd_q_daily_activity, "quarantine", "s_count")

# Effect on comments
ctd_itd_q_bsts_c_count <- intervention_bsts_effect(ctd_itd_q_daily_activity, "quarantine", "c_count")
```

```{r}
activity_its_plot(
    dt = ctd_itd_q_daily_activity,
    col_suffix = "dau",
    s_color = submission_users_color,
    c_color = comment_users_color,
    its_lm = ctd_itd_q_daily_activity_its_lm,
    intervention = "quarantine",
    y_lab = "# DAU",
    scale_labels = c("submission DAU", "comments DAU")
)
```

```{r}
# Effect on submission DAU
ctd_itd_q_bsts_s_dau <- intervention_bsts_effect(ctd_itd_q_daily_activity, "quarantine", "s_dau")

# Effect on comment DAU
ctd_itd_q_bsts_c_dau <- intervention_bsts_effect(ctd_itd_q_daily_activity, "quarantine", "c_dau")
```

#### Activity of Core Users W/O r/The_Donald

```{r}
activity_its_plot(
    dt = ctd_otd_q_daily_activity,
    col_suffix = "count",
    s_color = submission_color,
    c_color = comment_color,
    its_lm = ctd_otd_q_daily_activity_its_lm,
    intervention = "quarantine",
    y_lab = "# Posts",
    scale_labels = c("submissions", "comments")
)
```

```{r}
# Effect on submissions
ctd_otd_q_bsts_s_count <- intervention_bsts_effect(ctd_otd_q_daily_activity, "quarantine", "s_count")

# Effect on comments
ctd_otd_q_bsts_c_count <- intervention_bsts_effect(ctd_otd_q_daily_activity, "quarantine", "c_count")
```

```{r}
activity_its_plot(
    dt = ctd_otd_q_daily_activity,
    col_suffix = "dau",
    s_color = submission_users_color,
    c_color = comment_users_color,
    its_lm = ctd_otd_q_daily_activity_its_lm,
    intervention = "quarantine",
    y_lab = "# DAU",
    scale_labels = c("submission DAU", "comments DAU")
)
```

```{r}
# Effect on submission DAU
ctd_otd_q_bsts_s_dau <- intervention_bsts_effect(ctd_otd_q_daily_activity, "quarantine", "s_dau")

# Effect on comment DAU
ctd_otd_q_bsts_c_dau <- intervention_bsts_effect(ctd_otd_q_daily_activity, "quarantine", "c_dau")
```

```{r}
activity_its_plot(
    dt = ctd_otd_r_daily_activity,
    col_suffix = "count",
    s_color = submission_color,
    c_color = comment_color,
    its_lm = ctd_otd_r_daily_activity_its_lm,
    intervention = "restriction",
    y_lab = "# Posts",
    scale_labels = c("submissions", "comments")
)
```

```{r}
# Effect on submissions
ctd_otd_r_bsts_s_count <- intervention_bsts_effect(ctd_otd_r_daily_activity, "restriction", "s_count")

# Effect on comments
ctd_otd_r_bsts_c_count <- intervention_bsts_effect(ctd_otd_r_daily_activity, "restriction", "c_count")
```

```{r}
activity_its_plot(
    dt = ctd_otd_r_daily_activity,
    col_suffix = "dau",
    s_color = submission_users_color,
    c_color = comment_users_color,
    its_lm = ctd_otd_r_daily_activity_its_lm,
    intervention = "restriction",
    y_lab = "# DAU",
    scale_labels = c("submission DAU", "comments DAU")
)
```

```{r}
# Effect on submission DAU
ctd_otd_r_bsts_s_dau <- intervention_bsts_effect(ctd_otd_r_daily_activity, "restriction", "s_dau")

# Effect on comment DAU
ctd_otd_r_bsts_c_dau <- intervention_bsts_effect(ctd_otd_r_daily_activity, "restriction", "c_dau")
```

### Daily severe toxicity

```{r}
ctd_itd_daily_sev_tox <-  daily_sev_tox(ctd_itd_comments)
ctd_otd_daily_sev_tox <-  daily_sev_tox(ctd_otd_comments)

ctd_itd_q_daily_sev_tox <- ctd_itd_daily_sev_tox[created_date <= post_q_end_date]
ctd_otd_q_daily_sev_tox <- ctd_otd_daily_sev_tox[created_date <= post_q_end_date]
ctd_otd_r_daily_sev_tox <- ctd_otd_daily_sev_tox[created_date >= pre_r_start_date]

set_relative_week_and_day(ctd_itd_q_daily_sev_tox, quarantine_date)
set_relative_week_and_day(ctd_otd_q_daily_sev_tox, quarantine_date)
set_relative_week_and_day(ctd_otd_r_daily_sev_tox, restriction_date)
```

```{r, echo=FALSE}
# Interrupted Time Series

sev_tox_col_names <- c("median_sev_tox", "sev_tox_prop")
names(sev_tox_col_names) <- sev_tox_col_names
sev_tox_col_list <- as.list(sev_tox_col_names)

sev_tox_its_lm <- function(dt) {
  lapply(sev_tox_col_list, function(y_name) intervention_its_lm(dt, y_name))
}

ctd_itd_q_daily_sev_tox_its_lm <- sev_tox_its_lm(ctd_itd_q_daily_sev_tox)
ctd_otd_q_daily_sev_tox_its_lm <- sev_tox_its_lm(ctd_otd_q_daily_sev_tox)
ctd_otd_r_daily_sev_tox_its_lm <- sev_tox_its_lm(ctd_otd_r_daily_sev_tox)
```

#### Core Users W/I r/The_Donald

```{r}
sev_tox_its_plot(
  dt = ctd_itd_q_daily_sev_tox,
  col_name = "median_sev_tox",
  sevtox_its_lm = ctd_itd_q_daily_sev_tox_its_lm,
  intervention = "quarantine",
  y_lab = "Median severe toxicity"
)
```



```{r}
sev_tox_its_plot(
  dt = ctd_itd_q_daily_sev_tox,
  col_name = "sev_tox_prop",
  sevtox_its_lm = ctd_itd_q_daily_sev_tox_its_lm,
  intervention = "quarantine",
  y_lab = "Proportion with severe toxicity >= 0.5"
)
```

```{r}
ctd_itd_q_bsts_median_sev_tox <- intervention_bsts_effect(ctd_itd_q_daily_sev_tox, "quarantine", "median_sev_tox")
ctd_itd_q_bsts_sev_tox_prop <- intervention_bsts_effect(ctd_itd_q_daily_sev_tox, "quarantine", "sev_tox_prop")
```

#### Core Users W/O r/The_Donald

```{r}
sev_tox_its_plot(
  dt = ctd_otd_q_daily_sev_tox,
  col_name = "median_sev_tox",
  sevtox_its_lm = ctd_otd_q_daily_sev_tox_its_lm,
  intervention = "quarantine",
  y_lab = "Median severe toxicity"
)
```

```{r}
sev_tox_its_plot(
  dt = ctd_otd_q_daily_sev_tox,
  col_name = "sev_tox_prop",
  sevtox_its_lm = ctd_otd_q_daily_sev_tox_its_lm,
  intervention = "quarantine",
  y_lab = "Proportion with severe toxicity >= 0.5"
)
```

```{r}
ctd_otd_q_bsts_median_sev_tox <- intervention_bsts_effect(ctd_otd_q_daily_sev_tox, "quarantine", "median_sev_tox")
ctd_otd_q_bsts_sev_tox_prop <- intervention_bsts_effect(ctd_otd_q_daily_sev_tox, "quarantine", "sev_tox_prop")
```

The toxicity levels around the restriction seems to be greatly affected by the start of the George
Floyd protests (vertical black dashed line in the following plots), an exogenous factor.
For this reason, we also add a narrowed ITS regression of ±12 weeks (±84 days) that
excludes the protests, for comparison.

```{r}
ctd_otd_nr_daily_sev_tox <- ctd_otd_r_daily_sev_tox[created_day %in% -84:84]
ctd_otd_nr_daily_sev_tox_its_lm <- sev_tox_its_lm(ctd_otd_nr_daily_sev_tox)
```


```{r}
add_george_floyd_layers_to_sev_tox_plot(
  sev_tox_its_plot(
    dt = ctd_otd_r_daily_sev_tox,
    col_name = "median_sev_tox",
    sevtox_its_lm = ctd_otd_r_daily_sev_tox_its_lm,
    intervention = "quarantine",
    y_lab = "Median severe toxicity"
  ),
  ctd_otd_nr_daily_sev_tox_its_lm,
  "median_sev_tox"
)
```

```{r}
add_george_floyd_layers_to_sev_tox_plot(
  sev_tox_its_plot(
    dt = ctd_otd_r_daily_sev_tox,
    col_name = "sev_tox_prop",
    sevtox_its_lm = ctd_otd_r_daily_sev_tox_its_lm,
    intervention = "intervention",
    y_lab = "Proportion with severe toxicity >= 0.5"
  ),
  ctd_otd_nr_daily_sev_tox_its_lm,
  "sev_tox_prop"
)
```


```{r}
ctd_otd_r_bsts_median_sev_tox <- intervention_bsts_effect(
  ctd_otd_r_daily_sev_tox, "restriction", "median_sev_tox"
)
ctd_otd_r_bsts_sev_tox_prop <- intervention_bsts_effect(
  ctd_otd_r_daily_sev_tox, "restriction", "sev_tox_prop"
)
ctd_otd_nr_bsts_median_sev_tox <- intervention_bsts_effect(
  ctd_otd_nr_daily_sev_tox, "narrowed_restriction", "median_sev_tox"
)
ctd_otd_nr_bsts_sev_tox_prop <- intervention_bsts_effect(
  ctd_otd_nr_daily_sev_tox, "narrowed_restriction", "sev_tox_prop"
)
```



## Quality of Shared Information

```{r}
td_s_mbfc <- sumission_mbfc_by_period(td_submissions, mbfc, "quarantine")
ctd_itd_s_mbfc <- sumission_mbfc_by_period(ctd_itd_submissions, mbfc, "quarantine")
ctd_otd_s_mbfc <- sumission_mbfc_by_period(ctd_otd_submissions, mbfc, "all")
```

### On r/The_Donald

```{r}
submission_mbfc_aggregation(td_s_mbfc, "general_bias")
```
```{r}
submission_mbfc_aggregation(td_s_mbfc, "political_bias")
```
```{r}
submission_mbfc_aggregation(td_s_mbfc, "accuracy")
```
### Core Users W/I r/The_Donald

```{r}
submission_mbfc_aggregation(ctd_itd_s_mbfc, "general_bias")
```

```{r}
submission_mbfc_aggregation(ctd_itd_s_mbfc, "political_bias")
```
```{r}
submission_mbfc_aggregation(ctd_itd_s_mbfc, "accuracy")
```

### Core Users W/O r/The_Donald

```{r}
submission_mbfc_aggregation(ctd_otd_s_mbfc, "political_bias")
```

```{r}
submission_mbfc_aggregation(ctd_otd_s_mbfc, "general_bias")
```

```{r}
submission_mbfc_aggregation(ctd_otd_s_mbfc, "accuracy")
```

## R Session

```{r}
sessionInfo()
```

